Title Goes Here

### 2020-04-17 analysis/paper/paper.Rmd
add plots

@@

>>>>

fviz_pca_var(SYG6_xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))

@@

SYG_1 site data and analysis

# artifacts from SYG_1 site
library(stringr)
SYG_1df <- 
  df %>% 
  filter(str_detect(files, "SYG_1"))

SYG_1df_sitename <- SYG_1df %>% 
  mutate (files = str_remove_all(files, "A_|1|2|.tps")) %>% 
  separate (files, into = c("sitename", "files"), sep = "_") %>% 
  select (-files)

#list of all attributes without ID
SYG_1DF <- SYG_1df[,1:7]

#simpler way to calculate Correlataion, you can use
cor(SYG_1DF)

#a scatterplot matrix of Correlation
pairs(SYG_1DF)

# CV
map_df(SYG_1DF, cv)

SYG_1PCA <- prcomp(SYG_1DF, center = TRUE, scale = TRUE)

# remove stage 1 artefact
SYG_1xx_pca <- 
SYG_1df_sitename %>% 
  filter(SPstage.Stage != 1) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  prcomp(., center = TRUE, scale = TRUE)

SYG_1xx_pca1 <- 
  data.frame(SYG_1xx_pca$x,
             stage = as.factor( SYG_1df_sitename$SPstage.Stage[SYG_1df_sitename$SPstage.Stage !=1]))

#plot for both stage
SYG_1gg_stage <- 
ggplot(SYG_1xx_pca1 ,
       aes(PC1,
           PC2,
       colour = stage)) +
  geom_point() +
  stat_ellipse()

fviz_pca_var(SYG_1xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))
```

SYG_4 site data and analysis

# artifacts from SYG_4 site
library(stringr)
SYG_4df <- 
  df %>% 
  filter(str_detect(files, "SYG_4"))

SYG_4df_sitename <- SYG_4df %>% 
  mutate (files = str_remove_all(files, "A_|1|2|.tps")) %>% 
  separate (files, into = c("sitename", "files"), sep = "_") %>% 
  select (-files)

#list of all attributes without ID
SYG_4DF <- SYG_4df[,1:7]

#simpler way to calculate Correlataion, you can use
cor(SYG_4DF)

#a scatterplot matrix of Correlation
pairs(SYG_4DF)

# CV
map_df(SYG_4DF, cv)

SYG_4PCA <- prcomp(SYG_4DF, center = TRUE, scale = TRUE)

# remove stage 1 artefact
SYG_4xx_pca <- 
SYG_4df_sitename %>% 
  filter(SPstage.Stage != 1) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  prcomp(., center = TRUE, scale = TRUE)

SYG_4xx_pca1 <- 
  data.frame(SYG_4xx_pca$x,
             stage = as.factor( SYG_4df_sitename$SPstage.Stage[SYG_4df_sitename$SPstage.Stage !=1]))

#plot for both stage
SYG_4gg_stage <- 
ggplot(SYG_4xx_pca1 ,
       aes(PC1,
           PC2,
       colour = stage)) +
  geom_point() +
  stat_ellipse()

fviz_pca_var(SYG_4xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))
```
